\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Overcoming the Challenges of Teaching Cybersecurity in UK Computer Science Degree Programmes}

% BLIND Paper should be blinded
%\author{\IEEEauthorblockN{Tom Crick\IEEEauthorrefmark{1}, James
%    H. Davenport\IEEEauthorrefmark{2}, Paul Hanna\IEEEauthorrefmark{3}, Alastair
%    Irons\IEEEauthorrefmark{4} and Tom Prickett\IEEEauthorrefmark{5}} 
%\IEEEauthorblockA{\IEEEauthorrefmark{1}%School of Education, 
%Swansea University, Swansea, UK; Email: thomas.crick@swansea.ac.uk} 
%\IEEEauthorblockA{\IEEEauthorrefmark{2}%Dept.~Computer Science, 
%University of Bath, Bath, UK; Email: j.h.davenport@bath.ac.uk}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}, 
%Ulster University, Belfast, UK; Email: jrp.hanna@ulster.ac.uk}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}%Faculty of Technology, 
%Sunderland University, Sunderland, UK; Email: alastair.irons@sunderland.ac.uk}
%\IEEEauthorblockA{\IEEEauthorrefmark{5}%Dept.~Computer\&Information Sciences, 
%Northumbria University, Newcastle upon Tyne, UK; Email: tom.prickett@northumbria.ac.uk}}
\maketitle

\begin{abstract}
This Innovative Practice Full Paper explores the diversity of challenges relating to the teaching of
cybersecurity in UK higher education degree programmes, through the lens of national policy, to the
impact on pedagogy and practice. An article published in the Harvard Business Review in August 2019
argued that \textit{"Every Computer Science Degree Should Require a Course in Cybersecurity "}; in the UK, universities -- alongside government, industry and professional engineering bodies -- have been
championing this over recent years, focusing on computer science and cognate undergraduate degrees
programmes; one such professional body (BCS, The Chartered Institute for IT) has been mandating this
in accredited undergraduate degree programmes since 2015. Delivering cybersecurity effectively across
general computer science programmes presents a number of challenges related to pedagogy,
resources, faculty and infrastructure, as well as responding to industry requirements.

There is a serious demand for cybersecurity specialists, both in the UK and globally (estimates vary, but are always large – and increasing); there is thus significant and growing higher education provision
related to specialist undergraduate and postgraduate courses focusing on varying aspects of
cybersecurity (for example, cryptography, computer security, networks, digital forensics, ethical hacking, etc). To make our digital systems and products more secure, all in IT need to know some cybersecurity — thus, there is a case for depth as well as breadth; this is not a new concern, but it is a growing one. Computer science and cognate engineering disciplines are evolving to meet these demands -- both at school-level, as well as at university -- however, doing so is not without challenges. This paper explores the progress made to date in the UK, building on previous work in cybersecurity education and accreditation by highlighting key challenges and opportunities, as well as identifying a number of
enhancement activities for use by the international cybersecurity education community. It frames these
challenges through concerns with the quality and availability of underpinning educational resources, the
competencies and skills of faculty (especially focusing on pedagogy, progression and assessment), and
articulating the necessary technical resources and infrastructure related to delivering rigorous
cybersecurity content in general computer science and cognate degrees.

Though this critical evaluation of an emerging national case study of cybersecurity education in the UK,
we also present a number of recommendations across policy and practice -- from pedagogic principles
and developing effective cybersecurity teaching practice, challenges in the recruitment, retention and
professional development of faculty, to supporting diverse routes into post-compulsory cybersecurity
education (and thus, diverse careers) -- to provide the foundation for potential replicability and portability to other jurisdictions contemplating related education and skills reform initiatives and interventions.
\end{abstract}

\begin{IEEEkeywords}
cybersecurity, computer science education, curricula, accreditation, UK
\end{IEEEkeywords}

\section{Introduction}\label{sec:intro}
An article published in the Harvard Business Review in August 2019 argued that ``{\emph{Every Computer Science Degree Should Require a Course in Cybersecurity}}''\cite{cable_2019}; in the UK, universities
--- alongside government, industry and professional bodies -- have been championing this over recent years, focusing on computer science and cognate undergraduate degrees programmes. One professional body --- BCS, The Chartered Institute for IT --- has been mandating this in accredited undergraduate degree programmes since 2015\cite{Cricketal2019}. Delivering cybersecurity effectively across general computer science programmes presents a number of challenges related to pedagogy, underpinning educational resources, available skills and technical resources. This paper explores the progress to date, as well as a starting call to arms to the UK higher education sector by highlighting a number of future challenges and opportunities.

As part of its promotion of sustainability, the United Nations(UN) defines ''{\em{UN Sustainability Goal 9: Build resilient infrastructure, promote sustainable industrialization and foster innovation}}'' \cite{UNgoal9}. For our computing technology infrastructure to be secure we need to maintain and enhance cybersecurity. To achieve that we need to grow cybersecurity knowledge. As such the enhancement of cybersecurity education contributes directly to enhancing sustainability..

% Question we mix first and third person? Which should we use?

%\section{Background}
\section{Pedagogic Principles}
%To do - what are the key points?
%technical and not technical skills?%

Though it is generally thought of as part of computing, cybersecurity is actually a multidisciplinary ``subject'', or, in the words of \cite{Parrishetal2018a} a \emph{meta-discipline}. This point has been made several times, e.g.  in \cite{Stockman2013}, who described integrating Criminal Justice and Political Science into the study of cybersecurity.  
\subsection{Academic skills}\label{sec:academic}
If we look at the academic skill sets that a good Chief Information Security Officer should have, we can break them into three rough groupings.
\begin{itemize}
\item{\bf Psychology:} While the authors would not necessarily go as far as PurpleSec, who claim \cite{PurpleSec2020a} that ``98\% of cyber attacks rely on social engineering'', it is quite clear that a very large proportion do: not least the attacks classified as ``phishing'', ``spear-phishing'' and ``whaling''. The technical skills required to go phishing are minimal: being able to write
\begin{verbatim}
<a href="bad url">good url</a>
\end{verbatim}
generally suffices, and even that can be bought in.  Forging e-mail addresses is generally needed as well if one is to go spear-phishing. But the real skill comes in knowing what will get under people's radar.
\par
To defend against phishing, to inculcate good password habits\footnote{Whatever those might be: opinions vary and well-known pundits (e.g. \cite{Grimes2019b}) will disagree with NIST's advice \cite{NIST2019e}.} and much more depends on understanding, or at least following the advice of those who understand, the psychology of the user \cite{InglesantSasse2010a}. In particular it is imprtant not to fall into the ``users are the enemy'' trap \cite{AdamsSasse1999}.
\item{\bf Managerial:} Clearly the CISO has to manage the team. But there is much more than that. The CISO has to be a team player within top management. The CISO is responsible for the Cybersecurity Incident Response Plan. But \cite{Secureworks2019a} lists among its major flaws in CIRPs that they are lacking organisational support and buy-in:
\begin{itemize}
\item Plan sponsor lacks appropriate authority
(e.g., Executive Leadership Team, CIO, CTO, CISO);
\item Incident stakeholders do not know the plan exists;
\item Was developed unilaterally by a single business unit;
\item Roles and responsibilities for non-technical teams are vague.
\end{itemize}
All of these are managerial failings.
\item{\bf Technical:} there are of course many technical things that a CISO needs to be on top of.  They feature in the list \cite{Beaver2017a} of ``10 Essential Elements for Success as an Information Security Professional'' as ``(6) Find your specialty; (7) Maintain your technical edge; (8) Constantly improve your methodologies''.

These technical skills tend to be the ones that a Computer Science Department is best at teaching, though even here there are challenges --- see section \ref{practice}. One specific question is ``how much cryptography need a security expert know''. The classic answer is ``enough not to be dangerously ignorant, and not enough to be dangerously knowledgeable'', which is true but not helpful: see \S\ref{sec:second}.
\end{itemize}
\subsection{Human skills}\label{sec:human}
Besides the subject-specific skills mentioned above, there are also the human, or `soft', skills. It could be argued (e.g. \cite{Palkar2013a}) that these are underrated throughout computing education, but they are certainly necessary in cybersecurity.
\cite{Froehlich2019a} stresses them for the CISO, but the same is true throughout the cybersecurity industry. See also \cite{InfoSec2019a} --- obviously they have an axe to grind, but the message resonates with much the authors have heard, an agrees with the Wall Street Journals Cybersecurity Executive Forum \cite{WallStreetJournal2018c}. Their list of ``top five skills'' is this.
\begin{enumerate}
\item    Problem-solving;
\item    Communication;
\item    Analytical thinking;
\item    Collaboration/teamwork;
\item    Attention to detail.
\end{enumerate}

A Computer Science Department  would probably like to think that it taught most of these. Certainly a BCS-accredited one has to teach collaboration/teamwork, as that is a long-standing requirement for accreditation, despite the students' dislike of it \cite{Cricketal2020a}. However, there are doubts about the depth to which these are done, compared with industry's demands. Notably the collaboration required in cybersecurity is generally part of a multi-function team, rather than the group software engineering activity that tends to be the response to the demand to teach group working. Similarly the problem-solving required is that of being faced with an underspecified problem: ``it looks like we've been hacked'', but with a vast amount of information, most of it irrelevant.
%What else?

It is generally hard to make students take the development of these skills seriously, especially as they are hard to assess in the rigorous way computer scientists (staff and students) are used to. The authors' approaches to this is described in section \ref{sec:authors}.
\section{Developing effective cybersecurity teaching practice}\label{practice}

What is the most appropriate way to teach cybersecurity? \cite{Weiss:2013:THC:2527148.2527180} highlights there are benefits from teaching this in a practical manner. Real world case studies can be employed \cite[e.g.]{BritishAirways2018a,Zoom2020a}. Use can be made of guest lectures by industrialists to share practical insights and hence providing students with micro-exposure to the world of work is another positive contribution. One further approach is the inclusion of appropriate cybersecurity standards within the curricula.

The PCI DSS \cite{PCI2018b} is one such standard that has been used in precisely this manner. PCI DSS underpins all processing of credit/debit cards. Nevertheless, it is very rarely mentioned in generalist computer scientist courses. This would not matter so much if everyone handling payments data were sent by their employers on an effective PCI DSS course. However, the payments business is now so spread across websites, often run by small and medium enterprises (SME), or non-specialists. Even larger enterprises are not immune: \cite{BritishAirways2018a} reports that the recent British Airways breach was caused by a failure to adhere to PCI DSS in website maintenance. Section \ref{sec:second} describes one way to bring PCI DSS to life in an assignment.

Another way of adopting a more practical pedagogy is by teaching cybersecurity through the lens of hacking or the hacker curriculum \cite{bratus2010teaching}. Such an approach facilitates students to be more experimental and creative in their exploration of the discipline and can have corresponding benefits for their engagement. 


\section{challenges in the recruitment, retention and professional development of faculty}\label{sec:staff}
It is well known that cybersecurity skills are in short supply, in both industry~\cite{Ackerman2019a} and academia~\cite{schneider2013,endicott2018searching}. The demand for cybersecurity skills in industry makes it difficult for academia to attract academics with knowledge, practical experience, research background and academic aspirations. As universities expand their cybersecurity provision it is not uncommon to find multiple jobs advertised at the same time. Recent example have included a professor of cybersecurity, two senior academic positions and two junior academic positions in one advert. There are other examples in the UK of cybersecurity lecturing jobs remaining unfilled for longer than a year; there are also examples of cybersecurity research groups moving en masse from one university to another.

% this survey is quite old now - something more recent the ESG 
For example, research into the state of IT conducted annually by Enterprise Strategy Group (ESG) has revealed that the skills gap in information security continues to widen and has doubled in the past five years; in 2014, 23\% of respondents to the survey stated that their organisation had a problematic shortage of information security skills -- this had climbed to 51\% at the beginning of 2018~\cite{ESG:2018}. Clearly, cybersecurity is an issue which is being felt across many industries and organisations, and is a concern which extends beyond IT leadership into the boardroom~\cite{Ackerman2019a}.

The ESG survey is international, but ESG have confirmed that the UK figures are very similar. In the UK, there has been a resurgence of job adverts to recruit academic staff with specialisms in cybersecurity over the past three years.

%TO DO - ?CPD?  See conclusions

\section{Quality of resources to support cybersecurity education?}
Effective teaching requires appropriate supporting resources. The extent to which appropriate resources are available and suitable will be evaluated next. This evaluation highlights a number of occasions when underpinning resources could be improved. 
\subsection{Underpinning resources}
The formal resources for Cybersecurity education are in reasonable shape given the inevitable fast-moving nature of the subject. The authors see \cite{Anderson2008} as a major work, though probably daunting as a extbook. It is dated, but a new edition is in preparation, and largely on the author's website. More recently a UK-funded project has produced the ``Cyber Security Body Of Knowledge'' \cite{Bristol2019a}. This is not intended as a textbook, but is a useful reference.

One gap in the educational resources is the absence, as far as the authors know, of a good answer to ``how much cryptography need a security expert know''.

More worrying is the problem described in \cite[\S IV.B]{Cricketal2019} --- the state of general computer science educational resources with respect to cybersecurity. In particular \cite{Drop2019} describes the poor state of database textbooks withrespect to SQL injection.  Despite the fact that SQL injection is theoretically well-understood, it is still a real problem today, tweny years after it was first described: 
\begin{quote}
Overall,
SQL Injection (SQLi) accounted for more than 72%
of all attacks when looking at all verticals during this
period [December 2017--November 2019]. \cite{Akamai2020a}
\end{quote}
\subsection{Provision of laboratories}
Delivering a practical take upon cybersecurity often requires specialist computing resources, certainly if any form of penetration testing/ethical hacking is to be taught. The traditional solution to this was a dedicated laboratory, generally not connected to the outside world (in the case of the UK, the JANET network)  in order not to breach the operating conditions of the network. In practice it will probably not even be directly connected to the university's internal network for the same reasons.  An upmarket version of such a laboratory is described in \cite{Abler2006}, though an adequate one can be build for roughly \pounds10,000 in capital costs.  The real problem, which many computer science departments in the UK will struggle with, is the technician (We use the term loosely. Quite often the labour gets dumped, inappropriately, on research students. This also causes problems with maintaining the knowledge base.) time to maintain it: lost passwords, trashed machines if the hacking escapes, etc., and the problems of keeping the underlying infrastructure up-to-date with security patches while not changing the target machines the students are practising against.

An interesting alternative is to host such a laboratory ``in the cloud'', as recommended by, for example, \cite{Salah2014a}. This would eliminate the capital expenditure (in favour of recurrent cloud costs, but these should be significantly less). The impact on technician/support time is less clear. Ideally it ought to be less, but a lot depends on the extent to which the cloud provider's authentication structure can be interfaced with the host university's: the second author is currently having problems here with an unrelated piece of teaching outsourcing.

Outsourcing to the cloud means that the students' ``hacking'' commands traverse the university's and the external networks, even though then are not ``commands'' until they reach the laboratory in the cloud. Different universities in the UK, even reading the same external network's (JANET's) policies, have different views on whether this is permissible.

%Commonly such a laboratory will be not directly connected to the JANET network in order not to breach the operating conditions of the network. This creates further challenges in the form of acquisition and maintenance of specialist laboratory provision. TO DO - could benefit from a reference.  JHD: how is the above?


%\section{Research Questions}

%\section{Research Approach}

%\section{Body - Structure here to do}

\section{Teaching Innovations}\label{sec:authors}
As introduced in section \ref{sec:intro}, teaching cybersecurity well for the workplace is more than about academic skills. However, it is very hard to motivate computer scientists to study pure human skills. This is far from being a feature of students, as \cite{Beaver2019c} observes.
\begin{quote}
Still, technical knowledge seems to trump everything. I've attended national and regional information security conferences that have sessions on security careers and the essential soft skills for cybersecurity success. They're not nearly as well attended as the sessions on cool and sexy topics like threat hunting, cryptocurrency and ransomware.
\end{quote}
Hence the ideal assignment in cybersecurity mixes the academic and human skills, preferably inseparably.

%TO DO I think  we need some signposting here. The next paragraph isnt quite right
%TO DO? Is considering this author by author the best way? I wonder if we should do
%Paul - use in recruitment
%Alastair - approaches for specialist security courses? Are these also apppropriate to CS?
%Then James / Tom approaches to inclusion in CS
How Cybersecurity is taught within mainstream computer science is evolving rapidly. A number of alternative approaches exist. In this section examples of effective practices are explored with the intention of surfacing innovations that could be considered for wider exploitation. In general terms two alternatives approaches can be effectively adopted: Cybersecurity can be primarily delivered in a single course / module / subject and then referred to in other courses / modules/ subjects as appropriate. Or the teaching and assessment can be distributed across the curricula. Both approaches can be effective and are represented in the provided examples representing both are considered. 


\subsection{Second Author}\label{sec:second} %JHD
%Question - should some context be added? Size of cohort? year of module?
In this case study the approach adopted is to primarily deliver the cybersecurity content within a single subject / module and then signpost relevant  cybersecurity issues in other subjects / modules as appropriate. The advantage of this is, cybersecurity becomes a significant curricula component, the importance of which is very visible to learners. However the downside, is that learners may be tempted to consider cybersecurity as a specialism, rather than something that should always be considered TO DO Add reference - there is a paper related to students not including in security unless told to.

This author teaches on a Cybersecurity module in a general computing degree. As such there is a wide range of backgrounds on the course. We asked in section \ref{sec:academic} ``how much cryptography need a security expert know''. The answer for this course is ``about 90 minutes worth'', which seems to cover the bases well enough: in particular enough on cryptographic hashing to underpin the lecture on password management.


Since Cybersecurity is a practical subject, much of the learning takes place through the coursework. The assessment for the module is structured with these weightings.
\begin{itemize}
\item[20]Class test --- basically a traditional examination. Normally a closed-book test, but this year, due to Covid-19, it will be sat by students who have dispersed, so will have to be open-book.
\item[30]Group presentation. The class divide themselves into groups of 4--5, and each group picks a topic from either the ``OWASP Top 10'' \cite{OWASP2017a} or the ``OWASP Mobile Top  10'' \cite{OWASP2016a} and does a presentation on it to the rest of the class.  In terms of the human skills identified in section \ref{sec:human}, this is meant to help with the communication and team-working skills. Indeed, Covid-19 and the consequent dispersal of the students has meant that they are also learning remote team working: an unexpected bonus.  The author has found that it is extremely important to share this rationale, and the evidence at \cite{WallStreetJournal2018c,InfoSec2019a,Beaver2019c} with them.  Industrial speakers are also asked to stress these points.
\item[50]The students have to analyse three different (i.e. different vendors and style) on-line purchases (or mock-purchases, they are allowed to use an invalid  credit card) made subject to PCI DSS, looking at the screen as the ordinary customer would see it, but also at the browser logs (HAR files) and network logs (Wireshark or equivalent). For each, they are asked the following.
\begin{enumerate}
\item With which websites does your browser communicate during the transaction? Are there any that worry you, or whose function you do not understand?
\item[*]Last year two different students, purchasing from two different UK-based sites, found \verb+yandex.ru+ appearing here.
\item Looking at the logs, to which sites does your payment card number get sent, and how is it protected in transit? You \emph{should} quote the relevant part of the logs, but \emph{should} replace the card number and any other identifying/sensitive data, e.g. by \verb+NNNN NNNN NNNN NNNN+, before quoting.
\item Looking at the HTML you have saved, do you feel confident you know what it is doing with your data?
\item How dependent is the HTML you have on the correct functioning of the DNS? In particular, could bad DNS results result in a security problem?\label{DNS}
\item What makes you think that the sum of money displayed to you is the sum that will be transmitted to your bank?
\end{enumerate}
Question \ref{DNS} is meant to help them realise the interconnected nature of today's Internet, and the hidden dependencies. They have had a lecture about the DNS, and in particular the recent wave of home router attacks  \cite[and others]{Balaji2020a}.
\par
In addition, they are asked these overall questions.
\begin{enumerate}
\item What have you learned about the security of your card data?
\item In particular, what did you learn from the logs/HTML that you could not have reasonably deduced as a shopper with no access to these?
\item How obvious is the security of the websites to the shopper?
\item How might the system be more transparent to the shopper?
\end{enumerate}
Questions 3 and 4 are really open-ended ``problem-solving'' questions, to which the author doesn't have a neat solution. This really frustrates students, who want to know ``the right answer'', but is much closer to reality.
\end{itemize}
\subsection{Third Author}\label{sec:third} %PH
Steganography is the art of hiding information in full view but its use pre-dates computers.  For example, the ancient Greeks used to shave a slave’s head, write a message on their skull and then allow the hair to grow before sending them on a journey to the receiver’s location \cite{Herodotus440}.  Bringing this ``secure transmission of data'' into the modern era, it is possible use steganography approaches to, for example, hide data within an image and transmit the modified image to a receiver without anyone noticing that the image has been altered.  It works by replacing the least significant bits of the colour of each pixel with the data you wish to transmit.  Whilst this does change the colour of individual pixels, in say a full 24-bit image (where there is 1 byte for each of the red, green and blue components), the change is almost imperceptible, even when viewed side by side with the original image.  Taking an image of 800x600 pixels, it is possible to ``secretly'' transmit 800*600 pixels * 3 bits of data or 180000 bytes.

This topic has been delivered as a ``Masterclass'' falling under promotion and recruitment activity for both local and international students.  Given this activity occurs prior to enrolment, it has the benefit of raising the importance of security issues among potential computer science students at the outset of their careers, as well as raising awareness of those who show some interest in computing but who ultimately take up other career paths.  It also allows the topic to be introduced in the context of fundamental computer science topics such as binary, programming (as an encoder and decoder are required) and how an image and indeed characters are represented within a computer.  The talk also covers broader aspects such as what type of information needs to be transmitted securely, why it is important to be able to transmit information securely, the risks associated with people other than the intended recipient gaining access to the information and hence the need to consider cybersecurity issues when designing and developing computer systems.  Introducing security issues in the context of these traditional topics, ``mainstreams'' them, and hence raises their perceived importance among ``tomorrow’s students''.

\subsection{Fourth Author}\label{sec:fourth} % AI
%Do we need something on the size of the courses?
This author teaches on dedicated BSc and MSc courses in Cybersecurity. The author has employed a number of assessment instruments in cybersecurity to encourage students to use the assessment activities to enable student learning, described more fully in [blinded]. 
%BLIND \cite{Irons2019a}
The use of scenarios to encourage students to think both as attackers and defenders has been particularly helpful in enabling students to understand the cybersecurity environment. As an overall assessment strategy in cybersecurity attempts should be made to: 
\begin{itemize}
\item get students to identify and critically evaluate threats – ranging from nuisance threats to “advanced persistent threats”;
\item design, develop and implement strategies to counter the threats;
\item identify when breaches or attacks have taken place and critically evaluate the impact of those;
\item design, develop and implement approaches to recover from attack;
\item give students the opportunity to evaluate attacks and develop more robust cybersecurity defences as a result.
\end{itemize}

The above can be done in the context of specific cybersecurity scenarios or case studies, but can also be utilised to encourage students to think about and present policies and procedures for cybersecurity environments. 

One particular assessment task that has been used by the author which helps pull together many of the cybersecurity threads and complexities is the use of ``infographs''. An extract from an assessment using infographs is given below.
\begin{quote}
The cybersecurity environment is a wide and complex one. For the first part of this assignment you are required to produce an infograph (1 page) outlining the typical threats that either a) individuals in society or b) organisations face from breaches of cybersecurity. The design of your infograph and the content of the infograph is left to you to decide but you should consider visual impact, key messages, data to support, examples and underpinning research. You will have the chance to present your infograph to your peers, academics and guests from industry. You should be able to discuss the points raised on your infograph, explaining the detail and answering any questions asked. 
\end{quote}
As well as allowing the student to analyse and evaluate a particular issue or concern the assessment enables the development and assessment of a series of professional competencies (see section \ref{sec:human}), including communication, presentation skills, and the summarising of complex cybersecurity issues. 

\subsection{Fifth Author}\label{sec:fifth} % TP

This example refers to an academic who teaches Cybersecurity to general computer science undergraduate students at university in the United Kingdom . The BSc(Hons) Computer Science programme has an intake of about 240 students. The students upon the programme study a foundation of computer science for the first two years of their study before specialising in Internet of Things, Web Development, Games Development or Artificial Intelligence. This generic structure is fairly typical of Computer Science degree programmes delivered in the United Kingdom.

Rather than have a module dedicated to cybersecurity the teaching and assessment of the cybersecurity is embedded across the curricula as shown in ~\ref{tab:CaseStudy5}. The rationale for this is, cybersecurity becomes integral and learners are encouraged  to consider cybersecurity as something that should always be considered as part of normal practice. The consequence is that none of the individual modules/subjects or their related assessments are entirely related to cybersecurity (e.g. In an exam, a few questions will be cybersecurity related rather than the whole examination). If this is evaluated pessimistically, then learners could consider cybersecurity as a peripheral issue, however experience of the approach indicate this has not been the case.

\begin{table*}[ht]
	\caption{Cyber Security Curricula Coverage Case Study 5}{%
		\begin{tabular}{|p{3cm}|p{1cm}|p{6.5cm}|p{6.5cm}| }
			\hline
			Subject / Module & Year & Taught & How Assessed \\
			\hline
			Web Technologies & 1 & Confidentiality, integrity and availability. Threats and Attacks, how they materialise and how those attacks exploit website vulnerabilities. & Web page providing user training related to cybersecurity. \\
			\hline
			Systems Analysis & 1 & Personal, organisation and legal/regulatory framework in which a system can be used, including risks and constraints. & Self selected team Design Project \\
			\hline
			Databases & 1 & Threats and Attacks, how they materialise and how those attacks exploit database vulnerabilities. & Examination questions\\
			\hline
			Web Programming & 2 & Threats and Attacks, how they materialise and how those attacks exploit web vulnerabilities and approaches to mitigate. & A web application, secured again OWASP top ten vulnerabilities \\
			\hline
			Programming Design and Development & 2 & Design, defensive programming and testing & Programming project and related report\\
			\hline
			Networks, Operating Systems and Cybersecurity & 2 & Cybersecurity architecture and operations: physical and process controls that can be implemented across an organisation to reduce information and systems risk, identify, and mitigate the vulnerability, and ensure organisational compliance & Pratical work and related report\\
			\hline
			Team Project and Professionalism & 3 & Personal, organisation and legal/regulatory framework in which a system can be used, including risks and constraints. & Design and construction of a software component as part of a self selected team project and the evaluation of the project and its potential future exploitation. The projects are 'live' addressing the needs of a real client or problem. \\
			\hline
			\label{tab:CaseStudy5}
		\end{tabular}%
	}
\end{table*}

The approach taken is to emphasise the practical dimension of cybersecurity for the benefits advocated by ~\cite{Weiss:2013:THC:2527148.2527180}. To this end a Visiting Industrial Professor has been employed to support the viewpoint of industry in the design, delivery and assessment of the programme of study. The Visiting Industrial Professor is a senior industrialist specialising in cybersecurity and supports the department for 12 days of the academic year. During this time, the Visiting Industrial Professor advises upon context, develops and delivers classes, mentors students with interests in security careers and provides developmental support to academic colleagues. Student satisfaction questionnaires have been employed related to each of the interactions with students delivered by the Visiting Industrial Professor and whilst the completion rate remains low (less than 10 percent of the cohort, responses remains universally popular.) So not only is the use of a Visiting Industrial Professor ensuring the Cybersecurity content is industrially relevant, it is also popular with students. A third benefit of this approach, is the inclusion of cybersecurity has a very visible champion who raises awareness within the academic staff base, supports Continued Professional Development (CPD) of academics and helps ensures the cybersecurity is appropriately taught and assessed within the syllabus.

As can be seen from {\ref{tab:CaseStudy5}}, cybersecurity is integrated across the syllabus. The  large cohort of students studying the programme has quite a diverse range of interests. This harnessing of student creativity {\cite{Bradley2020}} is intended to enhance engagement with the discipline, when project work is completed,as much as possible students choose the subject of the project they undertake. Projects possible are limited by an appropriate set of constraints. In the context of the first year Systems Analysis module, teams of students engage in a research activities  to establish the scope of a system of their choosing. All projects are subject to university ethical approval which constraints the projects to those which are appropriate and achievable. A wide variety of systems are explored including games, web applications, mobile applications and so on. As part of this process students are required to explore and document the personal, organisation and legal/regulatory framework in which the system selected can be used, including risks and constraints related to its cybersecurity. The Industrial Professor, assists in briefing students and provides guidance on the general personal, organisation and legal/regulatory framework. Additionally, the Industrial Professor, is available to discuss the specific context of cybersecurity within the chosen projects. 

In the final year of their studies, all the students complete a team project with the Team Project and Professionalism subject. In this subject teams of students develop a software product of their own choosing. This is typically related to their chosen specialism. These projects must be live, normally addressing the needs of a real client but always addressing a real problem \footnote{A minority of students use the project to prototype a product they are considering using in a future business venture and a small number of other students address a research problem in collaboration with a university research group. However all projects involved the creation of a software product.}. A variety of products are developed for example games, web applications, mobile applications, wearable applications, computational intelligence solutions, IoT prototypes and so on. Teams of students are required to develop and then demonstrate a prototype application. This work forms a capstone to students studies and student are required to share their development via GITHub. They are encouraged to consider the work as a career portfolio element which in turn helps to evidence their capabilities to future employers. A number feedback that this has helped ensure them employment. The produced prototype and its future potential commercial exploitation are evaluated. The produced prototype, is expected to address personal, organisation and legal/regulatory framework in which the system they have selected can be used, including risks and constraints related to its cybersecurity. If there are limitations in this regard the students are expected to be abreast of them. Also, as part of this evaluation students are expected to evaluate the personal, organisation and legal/regulatory framework of the potential future exploitation of the project, including risks and constraints related to its cybersecurity. Similar guidance and support is provided by the visiting Industry Professor for the Team Project and Professionalism subject that was provided to System Analysis student, although it is in more depth and  sophisticated insights are expected (as well as evidence from the practical development work).  

As indicated, part of the rationale of this approach is to harness student creativity and hence raise engagement with the studies. As the assessment is divergent {\cite{Bradley2016}} (students are all completing different projects), the assessment reduces the opportunity to engage in academic misconduct as there would be little to be gained from fellow students work. The integrative manner in which cybersecurity is consider and considering as part of the capstone also raises the importance that students view cybersecurity. The rationale is to promote cybersecurity as something that needs to be always considered, not an optional extra. Feedback from students indicates, this emphasis upon building secure systems is of interest to employers and a common discussion point during employment interviews. Hence the appointment of the Visiting Industrial Professor is of benefit to academic staff, students and their future employers. It is also of benefit to the Visiting Professor as enables them to participate as an equal partner in an academic environment and hence gain valuable CPD.


\section{Conclusions and Further Work}

In the previous section, we see how some of the authors try to produce assignments which exercise both the academic and human skills needs. 

On the practical side, the community could do much to help itself in the way of sharing best practice.
\begin{enumerate}
\item Given the shortage of staff in the area (section \ref{sec:staff}), and the fact that universities have to teach this with less-than-ideally qualified staff, there is a real need for coordinated professional development in this area.
\item Sharing best  practice with respect to physical laboratories, especially reducing technical support effort.
\item The same for in-cloud laboratories.
\item At least in the UK, getting university lawyers to form a consistent view on the legitimacy of outsourcing cybersecurity laboratories to the cloud.
\end{enumerate}


\section*{Acknowledgement}

%The authors wish to thank Sally Pearce, Academic Accreditation Manager at BCS, The Chartered Institute for IT for supplying the summary information related to accreditation of UK degree programmes. Many people, accreditors and accredited, have contributed to accreditation practice in the UK (and elsewhere), and spreading good practice.

Removed for blind refereeing. %BLIND
%The first, second, fourth and fifth authors' institutions are members of the Institute of Coding, an initiative funded by the Office for Students (England) and the Higher Education Funding Council for Wales.

% The Fifth Author would like to thank the Royal Academy of Engineering (RAEng) for funding the Visiting Industrial Professor for three academic years.

%\section*{References}

\bibliographystyle{IEEEtran}
%\bibliography{security}
\bibliography{IEEEabrv,security}





\end{document}
